Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
reorg
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@82 43ef1190-90fd-4dd7-a769-d0121f02b80e

In many cases, this is sufficient. Sometimes, one engine can execute a
query an order of magnitude faster than another, in which case, there
is hardly reasonable doubt which is faster.

@@

These small differences may become important if they are systematic,
even if one engine is dramatically better than another in one case,
small deficiencies may add up to make the other a better choice for
most applications anyway.

@@

%\bibliographystyle{plain}
\bibliographystyle{plain-csmin}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

In many cases, this is sufficient. Sometimes, one engine can execute a
query an order of magnitude faster than another, in which case, there
is hardly reasonable doubt which is faster. Small differences may seem
unimportant but may become important if they are systematic. Even if
one engine is dramatically better than another in one case, small
deficiencies may add up to make the other a better choice for most
applications anyway.

@@

@@

%\bibliographystyle{plain}
%\bibliographystyle{plain-csmin}
\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}
